---
title: "Montgomery County Crash Reporting Data - Exploration and Visualization"
author: "Donald Dong, Michael Sanchez"
date: "Mar. 30, 2018"
output: html_document
---
<hr>
```{r global_options, include=FALSE}
knitr::opts_chunk$set(prompt=TRUE, comment="", echo=TRUE)
```
Get the crashing report data from 
[Montgomery County Government](https://data.montgomerycountymd.gov/Public-Safety/Crash-Reporting-Drivers-Data/mmzv-x632).
```{r }
dat <- read.csv("https://data.montgomerycountymd.gov/api/views/mmzv-x632/rows.csv")
```
# Exploration
```{r }
str(dat)
```
## ACRS Report Type 
```{r}
plot.ACRS.Report.Type <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    par(mar=c(5,12,5,2))
    barplot(t, horiz=TRUE, las=1, main="ACRS Report Type")
}
plot.ACRS.Report.Type(dat$ACRS.Report.Type)
```
<p>
In this data we didn't find anything unusual. 
There were three categories reported which consisted of Fatal Crash, Injury, and Property Damage Crash.
</p>
## Agency Name
```{r}
Agency.Name.raw <- dat$Agency.Name
plot.Agency.Name.raw <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    t <- head(t, 20)
    par(mar=c(5,12,5,2))
    barplot(t, horiz=TRUE, las=1, main="Agency Name (Raw)")
}
plot.Agency.Name.raw(Agency.Name.raw)

process.Agency.Name <- function(feature) {
    #' Process Agency Names
    #'      keep top 3 agency names, combine the rest into `Other`
    #'
    #' @param feature The raw Agency Names from the data set
    #' @return vector of string.
    keep <- names(head(sort(table(feature), decreasing=TRUE), 3))
    result <- vector(mode="character", length=length(feature))
    for (i in 1:length(feature)) {
        if (feature[i] %in% keep) {
            result[i] = as.character(feature[i])
        } else {
            result[i] = "Other"
        }
    }
    return(result)
}
Agency.Name <- process.Agency.Name(Agency.Name.raw)

plot.Agency.Name <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    t <- head(t, 20)
    par(mar=c(5,12,5,2))
    barplot(t, horiz=TRUE, las=1, main="Agency Name")
}
plot.Agency.Name(Agency.Name)
```
<p>
When we looked at the Agency Name feature, we found that there were more than 4 agencies involved; therefore, we decided to keep the top three agencies and gather the rest into an additional category named Other. Montgomery County Police was the top agency involved in the reports.
</p>
## Circumstance
```{r}
plot.Circumstance.raw <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    t <- head(t, 15)
    par(mar=c(4,15,4,2))
    barplot(t, horiz=TRUE, las=1, main="Circumstance (Raw, top 15)")
}
Circumstance.raw <- dat$Circumstance
plot.Circumstance.raw(Circumstance.raw)

process.Circumstance <- function(feature) {
    #' Process Circumstance
    #'      split the circumstance by comma
    #'
    #' @param feature The raw Circumstance from the data set
    #' @return hast table A table where key is the circumstance, value is a vector of row id.
    circ <- new.env(hash=TRUE)
    for (i in 1:length(feature)) {
        tokens <- strsplit(as.character(feature[i]), ", ")[[1]]
        for (token in tokens) {
            if (is.null(circ[[token]])) {
                circ[[token]] = i
            } else {
                circ[[token]] = c(circ[[token]], i)
            }
        }
    }
    return(circ)
}
Circumstance <- process.Circumstance(Circumstance.raw)

plot.Circumstance <- function(feature) {
    keys <- ls(feature)
    t <- vector()
    for (i in 1:length(keys)) {
        t[keys[i]] = length(feature[[keys[i]]])
    }
    t <- head(sort(t, decreasing=TRUE), 10)
    par(mar=c(4,15,4,2))
    barplot(t, horiz=TRUE, las=1, main="Circumstance (top 10)")
}
plot.Circumstance(Circumstance)
```
<p> 
In the Circumstance feature we found that most categories had the word N/A included so we went ahead and stripped that away. Once our data was cleaned, we clearly see that other than the N/A's, the circumstances that followed had to do with water/moist.
</p>
## Collision Type
```{r}
plot.Collision.Type.raw <- function(feature) {
  t <- sort(table(feature), decreasing=TRUE)
  par(mar=c(5,12,5,2))
  barplot(t, horiz=TRUE, las=1, main="Collision.Type (raw)")
}
plot.Collision.Type.raw(dat$Collision.Type)

process.Collision.Type <- function(feature) {
  #' Process Light
  #'      keep top 2 Light categories, combine the rest into `Light Not Perfect`
  #'
  #' @param feature The raw Light from the data set
  #' @return vector of string.
  keep <- names(head(sort(table(feature), decreasing=TRUE), 2))
  other <- c("OTHER", "UNKNOWN", "N/A")
  single <- "SINGLE VEHICLE"
  left <- c("OPPOSITE DIR BOTH LEFT TURN", "SAME DIR BOTH LEFT TURN", "SAME DIR REND LEFT TURN", "ANGLE MEETS LEFT TURN", "SAME DIRECTION LEFT TURN")
  right <- c("SAME DIR REND RIGHT TURN", "ANGLE MEETS RIGHT TURN", "SAME DIRECTION RIGHT TURN")
  head.On <- c("HEAD ON", "HEAD ON LEFT TURN", "ANGLE MEETS LEFT HEAD ON")
  sideswipe <- c("OPPOSITE DIRECTION SIDESWIPE", "SAME DIRECTION SIDESWIPE")
  result <- vector(mode="character", length=length(feature))
  for (i in 1:length(feature)) {
    if (feature[i] %in% keep) {
      result[i] = as.character(feature[i])
    } else if (feature[i] %in% single) {
      result[i] = "SINGLE"
    }else if (feature[i] %in% head.On) {
      result[i] = "HEAD ON"
    } else if (feature[i] %in% other) {
      result[i] = "OTHER"
    }else if (feature[i] %in% left) {
      result[i] = "LEFT"
    }else if (feature[i] %in% right) {
      result[i] = "RIGHT"
    } else if (feature[i] %in% sideswipe) {
      result[i] = "SIDESWIPE"
    }
  }
  return(result)
}
Collision.Type <- process.Collision.Type(dat$Collision.Type)

plot.Collision.Type <- function(feature) {
  t <- sort(table(feature), decreasing=TRUE)
  par(mar=c(5,12,5,2))
  barplot(t, horiz=TRUE, las=1, main="Collision Type")
}
plot.Collision.Type(Collision.Type)
```
<p> 
Under the Collision feature, we found that there were multiple combinations of vehicles so we decided to gather them in similar categories. We decided to gather all those accidents with any involvement turning left under the Left category and the same for Right, and Sideswipe. We kept the top two categories and gathered the Unknown's and N/A's with the category Other.
</p>
## Crash Date Time
```{r }
process.Crash.Date.Time <- function(feature) {
    #' Process Crash.Date.Times
    #'
    #' @param feature The raw Crash.Date.Times from the data set
    #' @return vector of datetime.
    feature <- as.character(feature)
    return (strptime(feature, "%m/%d/%Y %I:%M:%S %p", tz="EST5EDT"))
}
Crash.Date.Time <- process.Crash.Date.Time(dat$Crash.Date.Time)

plot.Crash.Date.Time <- function(feature) {
    v <- vector()
    for (i in 0:6) {
        for (j in 0:23) {
            v <- c(v, sum(feature$wday == i & feature$hour == j))
        }
    }
    m <- matrix(v, ncol=7, nrow=length(v) / 7)
    colnames(m) <- c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat")
    rownames(m) <- 0:23
    par(mar=c(5,5,10,5))
    heatmap(m, Rowv=NA, Colv=NA, col = heat.colors(256), scale="column", margins=c(5,5),
        ylab="Hour", main="Crash Weekday vs Hour")
}
plot.Crash.Date.Time(Crash.Date.Time)
```
<p>
I will do that.
</p>
## Driver Distracted By
```{r}
process.Driver.Distracted.By <- function(feature) {
    #' Process Driver Distracted By
    #'      keep top 3 distraction, combine the rest into `Other`
    #'
    #' @param feature The raw column from the data set
    #' @return vector of string.
    keep <- names(head(sort(table(feature), decreasing=TRUE), 3))
    result <- vector(mode="character", length=length(feature))
    for (i in 1:length(feature)) {
        if (feature[i] %in% keep) {
            result[i] = as.character(feature[i])
        } else {
            result[i] = "Other"
        }
    }
    return(result)
}
Driver.Distracted.By <- process.Driver.Distracted.By(dat$Driver.Distracted.By)

plot.Driver.Distracted.By <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    t <- head(t, 20)
    par(mar=c(5,15,5,2))
    barplot(t, horiz=TRUE, las=1, main="Driver Distracted By")
}
plot.Driver.Distracted.By(Driver.Distracted.By)
```
<p>
When analyzing this data, we realized that the number one reason for accidents was when the driver was not distracted. We went ahead and kept the top three reasons for the accident and gathered the rest into the Other category. This was done because the other values had very little effect in this data.
</p>
## Driver Substance Abuse
```{r}
process.Driver.Substance.Abuse <- function(feature) {
    #' Process Driver Substance Abuse
    #'      Merge the rest except for `NONE DETECTED` into `DUI`
    #'
    #' @param feature The raw column from the data set
    #' @return vector of string.
    keep <- "NONE DETECTED"
    other <- c("N/A", "OTHER", "UNKNOWN") 
    result <- vector(mode="character", length=length(feature))
    for (i in 1:length(feature)) {
        if (feature[i] == keep) {
            result[i] <- keep
        } else if (feature[i] %in% other) {
            result[i] <- "OTHER"  
        } else {
            result[i] <- "DUI"
        }
    }
    return(result)
}
Driver.Substance.Abuse <- process.Driver.Substance.Abuse(dat$Driver.Substance.Abuse)

plot.Driver.Substance.Abuse <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    par(mar=c(4,10,4,2))
    barplot(t, horiz=TRUE, las=1, main="Driver Substance Abuse")
}
plot.Driver.Substance.Abuse(Driver.Substance.Abuse)
```
<p>
In this feature we had a little over 10 values so we shrunk it down to 3. We kept the value Non detected as it was the number one value, followed by the other value which contained the unknown and N/A values. For the final value we gathered all the other values as we realized that they all fall under the driving under the influence category.
</p>
## Injury Severity
```{r}
plot.Injury.Severity <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    par(mar=c(5,15,5,2))
    barplot(t, horiz=TRUE, las=1, main="Injury Severity")
}
plot.Injury.Severity(dat$Injury.Severity)
```
<p>
This feature had 5 values in which the No apparent injury was the most reported.
</p>
## Light 
```{r}
process.Light <- function(feature) {
  #' Process Light
  #'      keep top 2 Light categories, combine the rest into `Light Not Perfect`
  #'
  #' @param feature The raw Light from the data set
  #' @return vector of string.
  keep <- names(head(sort(table(feature), decreasing=TRUE), 2))
  result <- vector(mode="character", length=length(feature))
  for (i in 1:length(feature)) {
    if (feature[i] %in% keep) {
      result[i] = as.character(feature[i])
    } else {
      result[i] = "Light Not Perfect"
    }
  }
  return(result)
}
Light <- process.Light(dat$Light)

plot.Light <- function(feature) {
  t <- sort(table(feature), decreasing=TRUE)
  par(mar=c(5,12,5,2))
  barplot(t, horiz=TRUE, las=1, main="Light")
}
plot.Light(Light)
```
<p>
In the Light feature we decided to gather the valued into three categories. We kept the value under Daylight and we
gathered those with some light under one category. Those values under unknown and N/A were added into the other
category.
</p>
## Location
```{r}
process.Location <- function(feature) {
    #' Process Locations
    #'      Parse the location into numeric lat and long, where lat has odd indices
    #'
    #' @param feature The raw Locations from the data set
    #' @return vector of numeric.
    feature <- as.character(feature)
    parse <- function(s) {
        tokens <- strsplit(s, ", ")
        x <- tokens[[1]][1]
        y <- tokens[[1]][2]
        x <- substr(x, 2, nchar(x))
        y <- substr(y, 1, nchar(y) - 1)
        return(c(as.numeric(x), as.numeric(y)))
    }
    return(sapply(feature, parse))
}
Location <- process.Location(dat$Location)

plot.Location <- function(feature) {
    library(ggmap)
    x <- feature[seq(1, length(feature), 2)]
    y <- feature[seq(2, length(feature), 2)]
    dat <- data.frame(long=y, lat=x) 
    map = get_map(c(mean(y), mean(x)), maptype="road", zoom=11)
    p = ggmap(map)
    p = p + geom_point(data=dat, aes(x=long,y=lat),
        color="red", size=0.2, alpha=0.2)
    p
}
plot.Location(Location)
```
<p>
In the Light feature we decided to gather the valued into three categories. We kept the value under Daylight and we gathered those with some light under one category. Those values under unknown and N/A were added into the other category 
</p>
## Surface Condition
```{r}
process.Surface.Condition <- function(feature) {
  #' Process Surface.Condition
  #'      keep top 2 surface conditions, combine the rest into `Other`
  #'
  #' @param feature The raw Surface.Condition from the data set
  #' @return hast table A table where key is the surface.Condition, value is a vector of row id.
  keep <- names(head(sort(table(feature), decreasing=TRUE), 2))
  result <- vector(mode="character", length=length(feature))
  for (i in 1:length(feature)) {
    if (feature[i] %in% keep) {
      result[i] = as.character(feature[i])
    } else {
      result[i] = "Other"
    }
  }
  return(result)
}
Surface.Condition <- process.Surface.Condition(dat$Surface.Condition)

plot.Surface.Condition <- function(feature) {
  t <- sort(table(feature), decreasing=TRUE)
  par(mar=c(5,12,5,2))
  barplot(t, horiz=TRUE, las=1, main="Surface.Condition")
}
plot.Surface.Condition(Surface.Condition)
```
<p>
to do
</p>
## Traffic.Control
```{r}
process.Traffic.Control <- function(feature) {
    #' Process Traffic.Controls
    #'      keep top 3 cats, combine the rest into `Other`
    #'
    #' @param feature The raw Traffic.Controls from the data set
    #' @return vector of string.
    keep <- c("NO CONTROLS", "TRAFFIC SIGNAL", "STOP SIGN")
    result <- vector(mode="character", length=length(feature))
    for (i in 1:length(feature)) {
        if (feature[i] %in% keep) {
            result[i] = as.character(feature[i])
        } else {
            result[i] = "Other"
        }
    }
    return(result)
}
Traffic.Control <- process.Traffic.Control(dat$Traffic.Control)

plot.Traffic.Control <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    par(mar=c(5,12,4,2))
    barplot(t, horiz=TRUE, las=1, main="Traffic Control")
}
plot.Traffic.Control(Traffic.Control)
```
<p>
to do
</p>
## Vehicle.Body.Type
```{r}
process.Vehicle.Body.Type <- function(feature) {
    #' Process Vehicle.Body.Types
    #'      keep `PASSENGER CAR`, combine the rest into `Other`
    #'
    #' @param feature The raw Vehicle.Body.Types from the data set
    #' @return vector of string.
    keep <- "PASSENGER CAR"
    result <- vector(mode="character", length=length(feature))
    for (i in 1:length(feature)) {
        if (feature[i] == keep) {
            result[i] = as.character(feature[i])
        } else {
            result[i] = "Other"
        }
    }
    return(result)
}
Vehicle.Body.Type <- process.Vehicle.Body.Type(dat$Vehicle.Body.Type)

plot.Vehicle.Body.Type <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    t <- head(t, 20)
    par(mar=c(5,15,5,2))
    barplot(t, horiz=TRUE, las=1, main="Vehicle Body Type")
}
plot.Vehicle.Body.Type(Vehicle.Body.Type)
```
<p>
to do
</p>
### Vehicle.Damage.Extent
```{r}
process.Vehicle.Damage.Extent <- function(feature) {
    #' Process Vehicle.Damage.Extents
    #'     combine `OTHER`, `N/A`, `UNKNOWN` into `Other`
    #'
    #' @param feature The raw Vehicle.Damage.Extents from the data set
    #' @return vector of string.
    combine <- c("OTHER", "N/A", "UNKNOWN")
    result <- vector(mode="character", length=length(feature))
    for (i in 1:length(feature)) {
        if (!feature[i] %in% combine) {
            result[i] = as.character(feature[i])
        } else {
            result[i] = "Other"
        }
    }
    return(result)
}
Vehicle.Damage.Extent <- process.Vehicle.Damage.Extent(dat$Vehicle.Damage.Extent)

plot.Vehicle.Damage.Extent <- function(feature) {
    t <- sort(table(feature), decreasing=TRUE)
    t <- head(t, 20)
    par(mar=c(5,10,4,2))
    barplot(t, horiz=TRUE, las=1, main="Vehicle Damage Extent")
}
plot.Vehicle.Damage.Extent(Vehicle.Damage.Extent)
```
<p>
to do
</p>
### Vehicle Movement
```{r}
process.Vehicle.Movement <- function(feature) {
  #' Process Vehicle Movment
  #'     Keep the top 5 feature, merge the result into `Other` 
  #'
  #' @param feature The raw Light from the data set
  #' @return vector of string.
  keep <- names(head(sort(table(feature), decreasing=TRUE), 5))
  result <- vector(mode="character", length=length(feature))
  for (i in 1:length(feature)) {
    if (feature[i] %in% keep) {
      result[i] = as.character(feature[i])
    } else {
      result[i] = "Other"
    }
  }
  return(result)
}
Vehicle.Movement <- process.Vehicle.Movement(dat$Vehicle.Movement)

plot.Vehicle.Movement <- function(feature) {
  t <- sort(table(feature), decreasing=TRUE)
  par(mar=c(5,12,5,2))
  barplot(t, horiz=TRUE, las=1, main="Vehicle.Movement")
}
plot.Vehicle.Movement(Vehicle.Movement)
```
<p>
to do
</p>
## Weather
```{r}
process.Weather <- function(feature) {
  #' Process Weatger
  #'      keep 3 categories, combine Foggy with cloudy,
  #'      add a `Severe` category
  #'      add an `Other` category
  #'
  #' @param feature The raw Weather from the data set
  #' @return vector of string.
  keep <- names(head(sort(table(feature), decreasing=TRUE), 2)) #here we process
  cloudy <- c("FOGGY", "CLOUDY")
  severe <- c("SNOW", "WINTRY MIX", "SLEET", "BLOWING SNOW", "SEVERE WINDS", "BLOWING SAND, SOIL, DIRT")
  result <- vector(mode="character", length=length(feature)) #length of the new vector
  for (i in 1:length(feature)) {
    if (feature[i] %in% keep) {
      result[i] = as.character(feature[i])
    } else if (feature[i] %in% severe) {
      result[i] = "SEVERE"
    } else if (feature[i] %in% cloudy) {
      result[i] = "CLOUDY"
    }else { 
      result[i] = "OTHER" 
    }
  }
  return(result)
}
Weather <- process.Weather(dat$Weather)

plot.Weather <- function(feature) {
  t <- sort(table(feature), decreasing=TRUE)
  par(mar=c(5,12,5,2))
  barplot(t, horiz=TRUE, las=1, main="Weather")
}
plot.Weather(Weather)
```
<p>
to do
</p>
# Combine features
## Bad weather
```{r}
plot.bad.weather <- function(location, weather) {
    library(ggmap)
    x <- location[seq(1, length(location), 2)]
    y <- location[seq(2, length(location), 2)]
    index <- weather != "CLEAR"
    x <- x[index]
    y <- y[index]
    w <- weather[index]
    dat <- data.frame(long=y, lat=x,weather=factor(w))
    map = get_map(c(mean(y), mean(x)), maptype="road", zoom=11)
    p = ggmap(map)
    p = p + geom_point(data=dat, aes(x=long,y=lat, colour=weather), size=0.4, alpha = 0.2)
    p
}
plot.bad.weather(Location, Weather)
```
## Crash Hour Location
```{r}
plot.Crash.Hour <- function(location, hour) {
    library(ggmap)
    x <- location[seq(1, length(location), 2)]
    y <- location[seq(2, length(location), 2)]
    dat <- data.frame(long=y, lat=x, hour=factor(hour)) 
    map = get_map(c(mean(y), mean(x)), maptype="road", zoom=11)
    p = ggmap(map)
    p = p + geom_point(data=dat, aes(x=long,y=lat, colour=hour), size=0.4, alpha = 0.2)
    p
}
plot.Crash.Hour(Location, Crash.Date.Time$hour)
```
## Driver Substance Abuse Injury Severity
```{r}
plot.Driver.Substance.Abuse.Injury.Severity <- function(serverity, substance) {
    t <- table(serverity, substance)
    u <- unique(serverity)
    barplot(t, beside = TRUE, col=topo.colors(length(u)))
    legend("topright", levels(u), col=topo.colors(length(u)), pch=19)
}
plot.Driver.Substance.Abuse.Injury.Severity(dat$Injury.Severity, Driver.Substance.Abuse)
```
<p>
to do
</p>
## Multiple Drivers Location
```{r}
plot.Multiple.Drivers <- function(Report.Number, location) {
    t <- table(Report.Number)
    i <- t > 2
    r <- rownames(t[i])
    index <- vector()
    for (n in Report.Number) {
        if (n %in% r) index <- c(index, TRUE)
        else index <- c(index, FALSE)
    }
    library(ggmap)
    x <- location[seq(1, length(location), 2)]
    y <- location[seq(2, length(location), 2)]
    x <- x[index]
    y <- y[index]
    dat <- data.frame(long=y, lat=x)
    map = get_map(c(mean(y), mean(x)), maptype="road", zoom=11)
    p = ggmap(map)
    p = p + geom_point(data=dat, aes(x=long,y=lat),
        color="red", size=0.2, alpha=0.2)
    p
}
plot.Multiple.Drivers(dat$Report.Number, Location)
```
<p>
to do
</p>
## Surface Condition Location
```{r}
plot.Surface.Condition <- function(location, condition) {
    library(ggmap)
    x <- location[seq(1, length(location), 2)]
    y <- location[seq(2, length(location), 2)]
    dat <- data.frame(long=y, lat=x, condition=factor(condition))
    map = get_map(c(mean(y), mean(x)), maptype="road", zoom=11)
    p = ggmap(map)
    p = p + geom_point(data=dat, aes(x=long,y=lat, colour=condition), size=0.4, alpha = 0.2)
    p
}
plot.Surface.Condition(Location, Surface.Condition) 
```
<p></p>
## Traffic Control Location
```{r}
plot.Traffic.Control <- function(location, condition) {
    library(ggmap)
    x <- location[seq(1, length(location), 2)]
    y <- location[seq(2, length(location), 2)]
    dat <- data.frame(long=y, lat=x, condition=factor(condition))
    map = get_map(c(mean(y), mean(x)), maptype="road", zoom=11)
    p = ggmap(map)
    p = p + geom_point(data=dat, aes(x=long,y=lat, colour=condition), size=0.4, alpha = 0.2)
    p
}
plot.Traffic.Control(Location, Traffic.Control)
```
<p>
to do
</p>
## Vehicle Body Type Location
```{r}
plot.Vehicle.Body.Type <- function(location, type) {
    library(ggmap)
    x <- location[seq(1, length(location), 2)]
    y <- location[seq(2, length(location), 2)]
    dat <- data.frame(long=y, lat=x, type=factor(type))
    map = get_map(c(mean(y), mean(x)), maptype="road", zoom=11)
    p = ggmap(map)
    p = p + geom_point(data=dat, aes(x=long,y=lat, colour=type), size=0.4, alpha = 0.2)
    p
}
plot.Vehicle.Body.Type(Location, Vehicle.Body.Type)
```
<p>
to do
</p>
## Vehicle Damage Extent Injury Severity
```{r}
plot.Vehicle.Damage.Extent.Injury.Severity <- function(serverity, extent) {
    t <- table(serverity, extent)
    u <- unique(serverity)
    barplot(t, beside = TRUE, col=topo.colors(length(u)))
    legend("topright", levels(u), col=topo.colors(length(u)), pch=19)
}
plot.Vehicle.Damage.Extent.Injury.Severity(dat$Injury.Severity, Vehicle.Damage.Extent)
```
<p>
to do
</p>
## Vehicle Movement Location
```{r}
plot.Vehicle.Movement <- function(location, movement) {
    library(ggmap)
    x <- location[seq(1, length(location), 2)]
    y <- location[seq(2, length(location), 2)]
    dat <- data.frame(long=y, lat=x, movement=factor(movement))
    map = get_map(c(mean(y), mean(x)), maptype="road", zoom=11)
    p = ggmap(map)
    p = p + geom_point(data=dat, aes(x=long,y=lat, colour=movement), size=0.4, alpha = 0.2)
    p
}
plot.Vehicle.Movement(Location, Vehicle.Movement)
```
<p>
to do
</p>
## Weather Injury Severity
```{r}
plot.Weather.Injury.Severity <- function(serverity, weather) {
    t <- table(serverity, weather)
    u <- unique(serverity)
    barplot(t, beside = TRUE, col=topo.colors(length(u)))
    legend("topright", levels(u), col=topo.colors(length(u)), pch=19)
}
plot.Weather.Injury.Severity(dat$Injury.Severity, Weather)
```
